### 2020-08-31 TCS_v3/08-conclusion.tex
piccoli cambi

We are currently investigating how to integrate our methodology
with other formal techniques to prove 
properties of the modeled systems, along the lines in~\cite{CFHOT15,OCHF16,BBGLBH2017}.
Moreover, we are considering possible enhancements of RSs based on entity mutation and on the possibility for two RSs to exchange entities.

@@

>>>>

We are currently investigating how to integrate our methodology
with other formal techniques to prove 
properties of the modeled systems, along the lines in~\cite{CFHOT15,OCHF16,BBGLBH2017,BBF15}.
Moreover, we are considering possible enhancements of RSs based on entity mutation and on the possibility for two RSs to exchange entities.

@@

\medskip

\noindent
{\small {\bf Acknowledgments}
We thank the anonymous reviewers for their detailed and very useful 
criticisms and recommendations that helped us to improve our paper.}
